---
title: "Pixels"
author: "Josh Hart"
date: "`r format(Sys.time(), '%B %d, %Y')`"
execute:
  keep-md: true
  warning: false
format:
  html:
    code-fold: true
    code-tools: true
---

## Background

Phones have always had a big impact on how people process the world. By understanding the brands with the highest popularity, we can understand their influence as well. By understanding popularity, we are capable of understanding what brand is more highly valued in society.

## Data Wrangling

```{r}
#| label: load_packages
#| echo: false

# Use this R-Chunk to load the libraries you will use in this file.
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(stringi)
```

```{r}
#| label: load_data

# Use this R-Chunk to import data.
phones = read.csv("https://query.data.world/s/mb5oi6cimqlpyf6bzpwvrgrr6id4pq?dws=00000")
```

```{r}
#| label: tidy_data

# Use this R-Chunk to clean & wrangle your data.
phones$Brand <- as.factor(phones$Brand)
phones <- phones %>%
  mutate(Discount = Discount.Percentage != 0)
phone <- select(phones, Product.Name, Brand, Number.Of.Reviews, Star.Rating, Discount)

filtered_text <- phone %>%
  filter(Number.Of.Reviews * (2 * Star.Rating) >= 0.5 * max(Number.Of.Reviews * (2 * Star.Rating)))
```

## Data Visualization

```{r, fig.height = 10, fig.width = 20}
#| label: plot_data

# Use this R-Chunk to plot & visualize your data.
ggplot(phone, aes(x = Brand, y = Number.Of.Reviews * (2 * Star.Rating), color = factor(Discount))) +
  geom_point() +
  geom_text(data = filtered_text, aes(label = Product.Name), vjust = -0.5, size = 3) +
  labs(title = "Popularity of Products by Brand and Discount",
       x = "Brand",
       y = "Popularity",
       color = "Discount") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom")
```



## Conclusions

From this data that was collected, we see that the brand that produces the most popularity is Redmi. This brand produces a similar amount of discounted and not discounted phone products. Not only that, but the higher popularity products were around the same value discounted or not. From this we understand that Redmi has the highest value in society and the most impact on it.
